Emitter Source Geolocation from Imparted Rotor Blade Modulation

### 2016-10-19 Radio_Propagation_Simulation.tex
add bold theory figure, add legends to verify figures

\section{Introduction}
%introduce the section and what will be discussed here
The simulation software is broken down into three main components, the radio wave propagation model, the scene model, and the ray tracing engine. The wave propagation model is a collection of equations that describe the physical phenomena that affect the propagation when represented by rays. The model used is based upon classical geometric optics to work with the ray tracing engine. The scene model is comprised of a 3D environment in order to define the physical rotor blade surface. The receiver and transmitter will also be defined in the same environment with simulated characteristics to match real life conditions. The ray tracing engine uses recursive execution described in \cite{Whitted1979}, replacing cameras and lights for receivers and transmitters respectively in a three dimensional environment.

\section{Radio Propagation Model}
%define the math behind the physical laws that are simulated within the simulation
The propagation model defined in this project is based on the following physical phenomena; free-space path loss, reflection, and the doppler effect. They are all formally established models described in full in \cite{Bertoni1999}, \cite{Parsons2000}, and \cite{Willis2005}. Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in 3D space and because of the assumptions made about the scene model.

\subsection{Free-Space Path Loss}
%describe path loss
Free-Space path loss is calculated using the Friis transmission and is incorporated into the model by keeping track of the distance a ray travels and adjusting its power is

@@

\subsubsection{Diffuse Reflection}
A perfect diffuse reflection, also known as Lambertian reflection, will reflect rays in all directions in a uniform hemisphere \cite{Sizun2005}. The hemisphere is centered at the point the ray hits, producing rays away from the surface. To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) \cite{Suffern2007}, \cite{Pharr2010}, \cite{Glassner1995}. There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation \cite{Phong:1998:ICG:280811.280980}. This method for the BRDF is regularly used in the rendering of computer graphics to simulate the reflection of light off surfaces and combines the diffuse and specular components. Since this was not designed for the longer wavelengths used in RF communications, an assumption is made about surface features. Where features relevant to light waves,  produce a reflectance distribution similar for this application.

@@

where $f_0$ is the initial transmitted frequency, $\lambda$ is the wavelength, $v_t$ is the velocity in the direction of the transmitter, and $v_r$ is the velocity in the direction of the reflection. This is similar to the Bistatic radar equation for Doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.

@@

where $\lambda$ is the wavelength of the transmitted signal based off of the speed of light $c$ and its initial frequency $f_0$

@@

%formula description
where $r$ is the radius along the length of the blade where the reflection occurs. $\omega_r$ is the angular velocity of the rotor. $\vec{d_p}$ is the normalized vector that is perpendicular to the rotor in its direction of travel and $\vec{d_t}$ is the normalized vector that is in the direction of the transmitted ray.

@@

\subsection{Rotor Blade}
%go over the shape of the blade
The rotor blade is the most complex object within the scene, due to its airfoil shape. The airfoil shape is designed to produce lift for the helicopter, and designing one is outside the scope of this project. Fortunately, there are databases that provide real helicopter airfoil designs in x,y coordinates. This data forms a 2D cross-section of the airfoil shape that will be extruded into the length of the rotor blade. Figure \ref{fig:airfoil} shows the airfoil cross-section that will be used to create the rotor surface.

@@

%go over how it is formed and the tessellation code
The 2D airfoil sections will form the ribs of the rotor blade but the surface of the blade will be made up of primitive surfaces to approximate the curved airfoil shape. The primitive shapes are triangles that span between the ribs and go around to cover the surface. This was done using a lightweight mesh generation method using a priori knowledge of the blade's shape. The designed algorithm, located in \ref{class_blade__surface_a160959f632ad73eff846aeea81aa84ae} $create\_surface()$ method, takes advantage of the object's uniform structure in 2D. The surface normals are then adjusted to match the correct directionality. Figure \ref{fig:tessilation} shows the created surface for the rotor blade that will be used in the scene.

@@

%modular parameters
All aspects of the rotor blade are parameterized. Starting with the airfoil shape, which is defined by a set of 2D coordinates. The length and the number of rib sections can be configured along with the number of blades and corresponding altitude. As well as the RPM. This allows the scene to replicate any type of rotor configuration and position it at a specific altitude.

\subsection{Transmitter}
%point source transmitter casting rays in specific direction
The transmitter is modeled as a point source, this means that all the radio waves are projected from this point into the scene. It is assumed that the transmitter is located on the ground within the x,y plane in relationship to the rotor blades. The transmitter is configured with a center frequency and is assumed to produce a tone at that frequency. Therefor, the signal produced has no inherent modulation applied to it.
%direction creation
Being that the transmitter is emitting radio waves into a 3D space, it is assumed to be transmitting in an omnidirectional fashion. But because the rotor and the receiver are the only two other objects within the scene, radio waves will only be propagated in their direction. This limitation allows for a higher concentration of rays to be casted, resulting in a higher resolution picture that eliminates computational overhead for the tracing engine. Figure \ref{fig:transmitter_direction} shows the rays, in blue, casted only in the vicinity of the rotor blade and receiver.

@@

\subsection{Receiver}
%physical receiver dimensions and antenna chars
The receiver object is modeled as a point in 3D space with a surrounding boundary layer in the shape of a sphere. This is because the receiver is assumed to have an omnidirectional antenna which will receive radio waves from all directions uniformly. The receiver will record any ray that hits the boundary layer within each frame of the simulation to create a sample of data at that instance in time.
%processing in each frame
The sample is produced using superposition of all the rays that are acting on the receiver at that instance in time which are then extrapolated to produce a clear result.
%realism
The receiver is configurable allowing the user to set a desired center frequency along with the sampling rate of the simulated hardware. The sampling rate will determine several simulation parameters in the ray tracer due to the need to associate this rate with the change in the rotor position for the next frame. The consequence of this is that increasing the sample rate will produce higher resolution results but, will increase the computational overhead of the simulation.

@@

\subsection{Computation}
%flow of the program
The ray tracing engine first sets up the environment, creating the surfaces and placing the objects in the scene. Then the number of frames that will be computed. The number of frames is determined by the number of rotations that the rotor makes within the simulation, the speed of the rotor in RPM and the sampling frequency of the receiver defined before the beginning of the simulation. This is described by

@@

%uniform disk equation
\begin{equation}
	v_{ray} = \begin{bmatrix}
			x \\
			y \\
			z \\
	\end{bmatrix}
	= \begin{pmatrix}
			\sqrt{r} \cos{\theta_u}  + d_x\\
			\sqrt{r} \sin{\theta_u}  + d_y \\
			d_z \\
	\end{pmatrix}
	\label{eqn:disk}
\end{equation}

The casting technique reduces the computation overhead by limiting the search space. It also creates a higher resolution result by focusing the limited number of rays in the direction of the other objects shown in figure \ref{fig:samp_method}.

@@

When a ray is casted into the scene it has an origin point, a direction vector, a frequency, and an initial power level. The ray then travels through the scene till it encounters another object. If there is a collision with the receiver it is recorded. If the ray collides with a rotor blade a new ray is calculated based on the normal of the geometric surface. The new ray's power is then updated as well as an updated frequency since the blade is moving. The power level is adjusted based on the BRDF of the specific material. Due to only the rotor and receiver being in the scene, rays that are found to hit the rotor are reflected, then a dedicated ray in the direction of the receiver is also calculated with a decayed power and adjusted frequency respective to the reflection.

>>>>

\section{Introduction}
%introduce the section and what will be discussed here
The simulation software is broken down into three main components; the radio wave propagation model, the scene model, and the ray tracing engine. The wave propagation model is a collection of equations that describe the physical phenomena that affect the propagation when represented by rays. The model used is based upon classical geometric optics to work with the ray tracing engine. The scene model is comprised of a 3D environment in order to define the physical rotor blade surface. The receiver and transmitter will also be defined in the same environment with simulated characteristics to match real life conditions. The ray tracing engine uses recursive execution described by Whitted in \cite{Whitted1979}, replacing cameras and lights for receivers and transmitters respectively in a three dimensional environment.

\section{Radio Propagation Model}
%define the math behind the physical laws that are simulated within the simulation
The propagation model defined in this project is based on the following physical phenomena; free-space path loss, reflection, fading, and the doppler effect. Which are all formally established models described in \cite{Bertoni1999, Parsons2000, Willis2005}. Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in 3D space and because of the assumptions made about the scene model.

\subsection{Free-Space Path Loss}
%describe path loss
Free-Space Path Loss is calculated using the Friis transmission and is incorporated into the model by keeping track of the distance a ray travels and adjusting its power by

@@

\subsubsection{Diffuse Reflection}
A perfect diffuse reflection, also known as Lambertian reflection, will reflect rays in all directions in a uniform hemisphere \cite{Sizun2005}. The hemisphere is centered at the point the ray hits, producing rays away from the surface. To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) \cite{Suffern2007, Pharr2010, Glassner1995}. There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation \cite{Phong:1998:ICG:280811.280980}. This method for the BRDF is regularly used in the rendering of computer graphics to simulate the reflection of light off surfaces and combines the diffuse and specular components. Since this was not designed for the longer wavelengths used in RF communications, an assumption is made about surface features. Where surface features, relevant to light waves,  produce a reflectance distribution similar for this application.

@@

where $f_0$ is the initial transmitted frequency, $\lambda$ is the wavelength, $v_t$ is the velocity in the direction of the transmitter, and $v_r$ is the velocity in the direction of the reflection. This is similar to the Bistatic radar equation for Doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the Doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.

@@

where $\lambda$ is the wavelength of the transmitted signal based off of the speed of light $c$ and its initial frequency $f_0$. The velocity in the direction of the transmitter is given by

@@

%formula description
where $r$ is the radius along the length of the blade where the reflection occurs. $\omega_r$ is the angular velocity of the rotor. $\vec{d_p}$ is the normalized vector that is perpendicular to the rotor in its direction of travel and $\vec{d_t}$ is the normalized vector that is in the direction of the transmitted ray. The velocity in the direction of the reflection is given by

@@

\subsection{Rotor Blade}
%go over the shape of the blade
The airfoil shape is designed to produce lift for the helicopter, and designing one is outside the scope of this project. Fortunately, there are databases that provide real helicopter airfoil designs in x,y coordinates. This data forms a 2D cross-section of the airfoil shape that will be extruded into the length of the rotor blade. Figure \ref{fig:airfoil} shows the airfoil cross-section that will be used to create the rotor surface.

@@

%go over how it is formed and the tessellation code
The 2D airfoil sections will form the ribs of the rotor blade but the surface of the blade will be made up of primitive surfaces to approximate the curved airfoil shape. The primitive shapes are triangles that span between the ribs and go around to cover the surface. This was done using a lightweight mesh generation method using knowledge of the blade's finished shape. The designed algorithm, located in \ref{class_blade__surface_a160959f632ad73eff846aeea81aa84ae} $create\_surface()$ method, takes advantage of the object's uniform structure in 2D. The surface normals are then adjusted to match the correct directionality. Figure \ref{fig:tessilation} shows the created surface for the rotor blade that will be used in the scene.

@@

%modular parameters
All aspects of the rotor blade are parameterized. Starting with the airfoil shape, which is defined by a set of 2D coordinates. The length and the number of rib sections can be configured along with the number of blades and corresponding altitude, as well as the RPM. This allows the scene to replicate any type of rotor configuration and position it at a specific altitude.

\subsection{Transmitter}
%point source transmitter casting rays in specific direction
The transmitter is modeled as a point source, this means that all the radio waves are projected from this point into the scene. It is assumed that the transmitter is located on the ground within the x,y plane in relation to the rotor blades. The transmitter is configured with a center frequency and is assumed to produce a tone at that frequency. Therefor, the signal produced has no inherent modulation applied to it.
%direction creation
Being that the transmitter is emitting radio waves into a 3D space, it is assumed to be transmitting in an omnidirectional fashion. The rotor and the receiver are the only two other objects within the scene, radio waves will only be propagated in their direction. This limitation allows for a higher concentration of rays to be casted, resulting in a higher resolution picture that eliminates computational overhead for the tracing engine. Figure \ref{fig:transmitter_direction} shows the rays, in blue, casted only in the vicinity of the rotor blade and receiver.

@@

\subsection{Receiver}
%physical receiver dimensions and antenna chars
The receiver object is modeled as a point in 3D space with a surrounding boundary layer in the shape of a sphere. This is because the receiver is assumed to have an omnidirectional antenna which will receive radio waves from all directions uniformly. The receiver will record any ray that hits the boundary layer within each frame of the simulation to create a sample of data at that instance in time.
%processing in each frame
The sample is produced using superposition of all the rays that are acting on the receiver at that instance, which are then extrapolated to produce a clear result.
%realism
The receiver is configurable which allows the user to set a desired center frequency along with the sampling rate of the simulated hardware. The sampling rate will determine several simulation parameters in the ray tracer due to the need to associate this rate with the change in the rotor position for the next frame. The consequence of this is that increasing the sample rate will produce higher resolution results but, will increase the computational overhead of the simulation.

@@

\subsection{Computation}
%flow of the program
The ray tracing engine first sets up the environment, creating the surfaces and placing the objects in the scene, then the number of frames that will be computed. The number of frames is determined by the number of rotations that the rotor makes within the simulation, the speed of the rotor in RPM and the sampling frequency of the receiver defined before the beginning of the simulation. This is described by

@@

%uniform disk equation
\begin{equation}
	v_{ray} = \begin{bmatrix}
			x \\
			y \\
			z \\
	\end{bmatrix}
	= \begin{pmatrix}
			\sqrt{r_u} \cos{\theta_u}  + d_x\\
			\sqrt{r_u} \sin{\theta_u}  + d_y \\
			d_z \\
	\end{pmatrix}
	\label{eqn:disk}
\end{equation}

where $r_u$ and $\theta_u$ are uniformly distributed random variables from $0 \leq r_u \leq BladeLength^{2}$ and $ 0 \leq \theta_u \leq 2\pi$ respectively.

The casting technique reduces the computation overhead by limiting the search space. It also creates a higher resolution result by focusing the limited number of rays in the direction of the other objects shown in Figure \ref{fig:samp_method}.

@@

When a ray is casted into the scene it has an origin point, a direction vector, a frequency, and an initial power level. The ray then travels through the scene till it encounters another object. If there is a collision with the receiver it is recorded. If the ray collides with a rotor blade a new ray is calculated based on the normal of the geometric surface. The new ray's power is then updated as well as an updated frequency since the blade is moving. The power level is adjusted based on the BRDF of the specific material. Due to only the rotor and receiver being in the scene, rays that are found to hit the rotor are reflected accordingly. Then a dedicated ray, in the direction of the receiver, is also calculated with a decayed power and adjusted frequency respective to the reflection.

### 2016-10-19 Ray_Tracing_Software.tex
add bold theory figure, add legends to verify figures

The ray tracing software developed during the course of the thesis is written in C++ in an XCode environment, but a generic implementation is provided to run on other operating systems. This code is loosely based on the work of Eric Degroot's developed for \cite{Groot2015} and implemented some modified base classes developed by him. It is a specific tool for analyzing the affects of rotor blade modulation on a signal tone, it does not provide generic 3D ray tracing in order to optimize the performance for this task. The software is provided without a GUI implementation and is run on different parameters by modifying the main.c file. This is due to the amount of parameters involved but could be easily extended to provide command line arguments in future iterations.

To use the software for performing RBM simulations there are several key parameters that are needed. First a file containing the points that define the 2D section of the airfoil shape, one default file is included in the software package for ease of use and as a template for other airfoil shapes.

the other key parameters that define the simulation are shown in Table \ref{tab:key_values}

@@

On Linux machines the code must first be built using make with the main file configured before hand. Then run the Raytracer3D executable.

>>>>

The ray tracing software developed during the course of the thesis is written in C++ in an XCode environment, but a generic implementation is provided to run on other operating systems. This code is loosely based on the work Eric Degroot developed for \cite{Groot2015} and implemented some modified base classes developed by him. It is a specific tool for analyzing the affects of rotor blade modulation on a signal tone, it does not provide generic 3D ray tracing in order to optimize the performance for this task. The software is provided without a GUI implementation and is run on different parameters by modifying the main.c file. This is due to the amount of parameters involved but could be easily extended to provide command line arguments in future iterations.

To use the software for performing RBM simulations there are several key parameters that are needed. First a file containing the points that define the 2D section of the airfoil shape, one default file is included in the software package for ease of use and as a template for other airfoil shapes. The other key parameters that define the simulation are shown in Table \ref{tab:key_values}

@@

On Linux machines the code must first be built using Make with the main file configured before hand. Then run the Raytracer3D executable.

### 2016-10-19 Results_new.tex
add bold theory figure, add legends to verify figures

\section{Introduction}
%introduce the results section and what processing will be done
The information gathered from the previous section is used to estimate the azimuth and elevation angles of the transmitter. First the azimuth angle will be estimated which will provide the information necessary for calculating the elevation angle. The results of the estimation techniques are then analyzed to determine their accuracy.

@@

From Figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. By computing the difference of the two

@@

where $Max Upper Envelope$ is an array of the maximum value of each upper envelope calculation, and $Min Lower Envelope$ is an array of the minimum value of each lower envelope calculation. $Envelope Difference$ is an almost exact sinusoid centered around zero, shown in Figure \ref{fig:azimuth_estimation_difference}.

@@

From Figure \ref{fig:peaks}  we see the two peaks denoted by the red x's, one at 90\textdegree \space and the other at  270\textdegree. Now we have a minimum value that should denote the 90\textdegree \space location and the two peak locations that denote the 90\textdegree \space and 270\textdegree \space locations. Because it is possible that the minimum could find the wrong peak for the 90\textdegree \space location we can compare the peak locations on the average power data, that was used to find the successive average during data collection, to determine which location is actually 90\textdegree.

@@

From there the Minimum method and the peak method can be compared to see if they agree on the 90\textdegree \space location. If this is not the case one will be chosen and the helicopter can fly in that direction and measure based on the physical movement of the helicopter or if the resulting envelope got larger or smaller because of the change in elevation angle.

@@

Then to find the elevation angle we look back at equation \ref{eq:theory_180_upper} swapping $MaxUpperEnvelope$ with $f_{DopplerCorrect(\theta_{Az})}$ because this is now over the azimuth range and swap $f_{DopplerMax}$ for $f_{Doppler_{R Estimate Max}}$ because we need the maximum doppler for the current reflection estimate. we then solve for the elevation angle

@@

If we now consider a pitched blade the above method for estimating Azimuth and elevation becomes inaccurate due to the increased Doppler between 90\textdegree \space and 270\textdegree \space and the decreased Doppler on the other side. To correct this error we need to correct both the difference calculation and the correct Doppler data accordingly. The uncorrected data is shown in Figure \ref{fig:diff_pitch_noCorrection} and \ref{fig:dop_pitch_noCorrection} with percent azimuth error of 20\% and percent elevation error of 35\%.

>>>>

\section{Introduction}
%introduce the results section and what processing will be done
The information gathered from the previous section is used to estimate the azimuth and elevation angles of the transmitter. First the azimuth angle will be estimated which will provide the information necessary for also calculating the elevation angle. The results of the estimation techniques are then analyzed to determine their accuracy.

@@

From Figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. We then take the difference

@@

where $Max Upper Envelope$ is an array of the maximum value of each upper envelope calculation, and $Min Lower Envelope$ is an array of the minimum value of each lower envelope calculation. The result is an almost exact sinusoid centered around zero, shown in Figure \ref{fig:azimuth_estimation_difference}.

@@

From Figure \ref{fig:peaks}  we see the two peaks denoted by the red x's, one at 90\textdegree \space and the other at  270\textdegree. Now we have a minimum value that should denote the 90\textdegree \space location and the two peak locations that denote the 90\textdegree \space and 270\textdegree \space locations. Since it is possible that the minimum could find the wrong peak for the 90\textdegree \space location we can compare the peak locations on the average power data, that was used to find the successive average during data collection, to determine which location is actually 90\textdegree.

@@

From there the minimum method and the peak method can be compared to see if they agree on the 90\textdegree \space location. If this is not the case one will be chosen and the helicopter can fly in that direction. The resulting Doppler can then be measured, based on the physical movement of the helicopter or if the resulting envelope, to confirm the correct 90\textdegree \space location.

@@

Then to find the elevation angle we look back at equation \ref{eq:theory_180_upper} swapping $MaxUpperEnvelope$ with $f_{DopplerCorrect(\theta_{Az})}$ because this is now over the azimuth range and swap $f_{DopplerMax}$ for $f_{Doppler_{R Estimate Max}}$ because we need the maximum doppler for the current reflection estimate. We then solve for the elevation angle

@@

If we now consider a pitched blade the above method for estimating azimuth and elevation becomes inaccurate due to the increased Doppler between 90\textdegree \space and 270\textdegree \space and the decreased Doppler on the other side. To correct this error we need to correct both the difference calculation and the correct Doppler data accordingly. The uncorrected data is shown in Figure \ref{fig:diff_pitch_noCorrection} and \ref{fig:dop_pitch_noCorrection} with percent azimuth error of 20\% and percent elevation error of 35\%.

### 2016-10-19 Simulation.tex
add bold theory figure, add legends to verify figures

\section{Analysis Techniques}
The data from the CSV files generated by the raytracing program are loaded into MATLAB scripts to process the data. The processing technique used is the spectrogram function that computes the short time Fourier transform. This allows for computations to be done in the time frequency domain and provides an accurate picture of how the signal is changing with time. Figure \label{fig:test_spec} shows an example of the computed spectrograms.

@@

After the computation of the short time Fourier transform; the Doppler envelope is calculated by performing a threshold on the power, in both the positive and negative Doppler, at each time slice. The envelope value for that time slice is found by approaching zero frequency and stopping as the power reaches a predetermined level from both the negative and positive values. The power level to set the threshold is calculated differently based on weather the elevation or the azimuth parameter is being swept. For the azimuth angle sweep, which will be shown later in section \ref{taa}, the maximum power is found in each time slice then those values are averaged. Then for each successive angle the same average is taken and averaged with all the others.

@@

Comparing Figure \ref{fig:rx_position_0m} with \ref{fig:rx_position_7m} the max Doppler reflects the information in Figure \ref{fig:rx_position} and the overall envelope is affected. The envelope in Figure \ref{fig:rx_position_0m} is much noisier than the envelope of Figure \ref{fig:rx_position_7m} and the envelope of this second figure has a more distinct shape with less variation between its two peaks. The position of the receiver will also determine whether the azimuth angle can be derived from the resulting signal shown later in section \ref{taa}. Therefore, the receiver will be offset from the center of rotation by 7 m for the subsequent simulations.

@@

In Figure \ref{fig:pitch_tx_elevation_angle} the max Doppler versus elevation angles are initially shifted up in frequency from a pitch of 0\textdegree \space and, consequently, have changed in slope. This is because the rays hitting the blades from below are reflecting into the receiver at an angle that is closer to the direction of blade travel. The interesting thing about this plot is that the pitch envelopes actually become closer to the 0\textdegree \space envelope as the elevation angle becomes smaller. Figure \ref{fig:pitch_tx_elevation_angle_difference} shows the difference plotted over elevation angle.

>>>>

\section{Analysis Techniques}
The data from the CSV files generated by the raytracing program are loaded into MATLAB scripts to process the data. The processing technique used is the spectrogram function that computes the short time Fourier transform. This allows for computations to be done in the time frequency domain and provides an accurate picture of how the signal is changing with time. Figure \ref{fig:test_spec} shows an example of the computed spectrograms.

@@

After the computation of the short time Fourier transform; the Doppler envelope is calculated by performing a threshold on the power, in both the positive and negative Doppler, at each time slice. The envelope value for that time slice is found by approaching zero frequency and stopping as the power reaches a predetermined level from both the negative and positive values. The power level to set the threshold is calculated differently based on whether the elevation or the azimuth parameter is being swept. For the azimuth angle sweep, which will be shown later in section \ref{taa}, the maximum power is found in each time slice then those values are averaged. Then for each successive angle the same average is taken and averaged with all the others.

@@

Comparing the received signal envelopes Figure \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m} the maximum Doppler increase reflects the information in Figure \ref{fig:rx_position}. The envelope in Figure \ref{fig:rx_position_0m} is also much noisier than the envelope of Figure \ref{fig:rx_position_7m} and the signal envelope, for the receiver is at 7 m, has a distinctive shape with less variation between its two peaks. The position of the receiver will also determine whether the azimuth angle can be derived from the resulting signal shown later in section \ref{taa}. Therefore, the receiver will be offset from the center of rotation by 7 m for the subsequent simulations.

@@

In Figure \ref{fig:pitch_tx_elevation_angle} the maximum Doppler versus elevation angles are initially shifted up in frequency from a pitch of 0\textdegree \space and, consequently, have changed in slope. This is because the rays hitting the blades from below are reflecting into the receiver at an angle that is closer to the direction of blade travel. The interesting thing about this plot is that the pitch envelopes actually become closer to the 0\textdegree \space envelope as the elevation angle becomes smaller. Figure \ref{fig:pitch_tx_elevation_angle_difference} shows the difference plotted over elevation angle.
